Testing the precision of Bangla Communication Scale: Item Response Theory Guided Analysis

### 2022-02-04 manuscript.Rmd
Validity description added

This study had fourth objectives. First, we confirmed the one factor solution of our scale obtained in Study-1. Second, to gather convergent validity evidence of BCS. For this, we calculated the bivariate correlation among the scores of Bangla Communication Scale and Bangla Hopeless Scale. Third, we established gender-based measurement invariance of Bangla Communication Scale.  Lastly, we assessed item discrimination, item difficulty and precision of BCS using Item Respons Theory Based Analysis

@@

>>>>

This study had fourth objectives. First, we confirmed the one factor solution of our scale obtained in Study-1 and estimated the reliability of the scale. Second, to gather convergent validity evidence of BCS. For this, we calculated the bivariate correlation among the scores of Bangla Communication Scale and Bangla Hopeless Scale. Third, we established gender-based measurement invariance of Bangla Communication Scale.  Lastly, we assessed item discrimination, item difficulty and precision of BCS using Item Respons eTheory Based Analysis

@@

### Measures

#### Bangla Rotter's I-E Scale

To confirm the latent structure of Bangla Communication scale, we used the one factor solution with 17 items obtained in our Study 1.

#### Bangla Beck Hopelessness Scale

```{r beck-hopelessness, include =F}
hopelessness<- validity.data.full %>% 
  dplyr::select( HS01:HS20) 
#ordinal alpha
hopelessness.alpha <- psych::alpha(hopelessness,check.keys=TRUE)

hopelessness.alpha <- hopelessness.alpha$total$raw_alpha
```

Beck Hopelessness Scale(BHS) is composed of 20 items with a  dichotomous response scale(True/False) [@beck1974measurement]. It captures three major dimensions of hopelessness: Feelings about the future, loss of motivation and expectations [@balsamo2020further]. This scale has nine reversed coded items (items 1, 3, 5, 6, 8, 10, 13, 15, 19) and yield a total score (range 0-20) where a higher score indicates higher disposition towards hopelessness. In this study we have used the Bangla Hopelessness scale [@uddinPsychometricEvaluationBangla]. Bangla Beck Hopelessness Scale retained all 20 items of the original scale and following the same scoring method. Internal consistency K-R coefficient for bangla BecK Hopelessness Scale in out Study-2 sample was `r apa(hopelessness.alpha,2,T)`
